Gammapy: A Python package for gamma-ray astronomy

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Cosimo Nigro <cosimonigro2@gmail.com>

\gammapy automatically generates a likelihood including three different types
of terms, two Poissonian likelihoods for the \fermi map and the
ON/OFF counts, and a $\chi^2$ accounting for the flux points. For \fermi, a 
three-dimensional forward folding of the sky model with the IRF is performed,
in order to compute the predicted counts in each sky-coordinate and energy bin.
For \magic, a one-dimensional forward-folding of the spectral model with the
\irfs is performed to predict the counts in each estimated energy bin. A log
parabola is fitted to the almost five decades in energy $10\,{\rm GeV} --
	300\,{\rm TeV}$. %% is the LP formula specified elsewhere?

@@

\subsection{Broadband SED Modeling}
\label{ssec:broadband-sed-modeling}
By combining \gammapy with astrophysical modelling codes, users can also fit
astrophysical spectral models to \gammaray data. In \gammaray
astronomy one typically observes two radiation production
mechanisms, the so-called hadronic and leptonic scenarios.
There are mutiple Python packages that are able to model
the \gammaray emission, given a physical scenario. Among those
packages are  \cite{agnpy}, \cite{naima}, \cite{jetset} or \cite{gamera}.
Tyically those emission models predict broadband emission from
radio waves up to the very high-energy \gammaray range.
By relying on the multiple dataset types in \gammapy those
data can be combined to constrain such a broadband emission model.
\gammapy provides a built-in \code{NaimaSpectralModel} that allows
users to wrap a given astrophysical emission model from the
"naima" package and fit it directly to \gammaray data.

>>>>

\gammapy automatically generates a likelihood including three different types
of terms, two Poissonian likelihoods for the \fermi map and the
ON/OFF counts, and a $\chi^2$ accounting for the flux points. For \fermi, a 
three-dimensional forward folding of the sky model with the IRF is performed,
in order to compute the predicted counts in each sky-coordinate and energy bin.
For \magic, a one-dimensional forward-folding of the spectral model with the
\irfs is performed to predict the counts in each estimated energy bin. A log
parabola is fitted to the almost five decades in energy $10\,{\rm GeV} -
	300\,{\rm TeV}$. %% is the LP formula specified elsewhere?

@@

\subsection{Broadband SED Modeling}
\label{ssec:broadband-sed-modeling}
By combining \gammapy with astrophysical modelling codes, users can also fit
astrophysical spectral models to \gammaray data. In \gammaray
astronomy one typically observes two radiation production
mechanisms, the so-called hadronic and leptonic scenarios.
There are mutiple Python packages that are able to model
the \gammaray emission, given a physical scenario. Among those
packages are  \cite{agnpy}, \cite{naima}, \cite{jetset} or \cite{gamera}.
Tyically those emission models predict broadband emission from
radio waves up to the very high-energy \gammaray range.
By relying on the multiple dataset types in \gammapy those
data can be combined to constrain such a broadband emission model.
\gammapy provides a built-in \code{NaimaSpectralModel} that allows
users to wrap a given astrophysical emission model from the
naima package and fit it directly to \gammaray data.
